---
title: "<center> <h1> **Shinyapp to monitor Covid-19 <br> Cases, Deaths, Recoveries and Vaccinations** </h1> </center>"
date:
output: 
  html_document:
runtime: shiny
editor_options: 
  chunk_output_type: console
---
<style type="text/css">

h1.title {
  font-size: 38px;
  color: mediumblue;
}



h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 28px;
  color: Red;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}

</style>


```{r echo=F, message=F, warning=F}
#install.packages("devtools")
#devtools::install_github("RamiKrispin/coronavirus", force = TRUE)
library(lubridate)
library(tidyverse)
library(readr)
library(plotly)
urlfile="https://raw.githubusercontent.com/RamiKrispin/coronavirus/master/csv/coronavirus.csv"
coronavirus <- read_csv(url(urlfile))

```

### The data pertaining to cases, death and recoveries is pooled from [**Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE)**](https://github.com/RamiKrispin/coronavirus). Vaccination data is pooled from [**Our world in data**](https://github.com/owid/covid-19-data/blob/master/public/data/vaccinations/README.md). Information about the app can be found on [**Statistics & R**](https://firasfneish-statistics-r.netlify.app/). 

### **Both sources update the data sets on a daily basis and the app pools data automatically.**

# **Daily summary of Covid-19 cases, recoveries and deaths** {.tabset}


```{r echo=F}
#renderTable(coronavirus[c(1:5), ] )

coronavirus <- coronavirus %>% mutate(month=as.factor(month(as.POSIXlt(coronavirus$date, format="%Y/%m/%d"))),
                                      year=as.factor(format(as.Date(coronavirus$date, format="%d/%m/%Y"),"%Y"))
)


countries_list <- c(levels(as.factor(coronavirus$country)))

Months <- c(levels(coronavirus$month))

years <- c(levels(coronavirus$year))


```



## **Since the pandemic started**

Summing up the all cases depending on the dates chosen.
```{r, echo=F}

inputPanel(
selectInput(inputId = "Ctr_Pandemic_start", 
                        label = "Country of interest",
                        choices = countries_list, selected = c("Germany", "France"), multiple = T   ),


dateRangeInput('dateRange_start_pandemic',
      label = 'Date range:',
      start = max(coronavirus$date, na.rm = T)-10, end = max(coronavirus$date, na.rm = T))


)



dat_overall_seit_pandemic_start <- reactive(
coronavirus %>% filter(  (country %in% c(input$Ctr_Pandemic_start)) &
                         (date>=input$dateRange_start_pandemic[1] & date<=input$dateRange_start_pandemic[2])
                        ) %>% group_by(country, type) %>% summarise(confirmed=sum(cases), death=sum(cases),   recovered=sum(cases)) %>% rename(overall_numbers=confirmed)  
)


renderPlot(
  
  dat_overall_seit_pandemic_start() %>% ggplot(aes(country, overall_numbers, fill=type, label=overall_numbers))+
    geom_bar(stat = "identity", position = "dodge")+
  geom_text(aes(label =overall_numbers , vjust=-0.5), position = position_dodge(width=0.9))+
    theme(axis.text.x = element_text(face = "bold", size = 18))+ ylab("Number of cases")+ 
    labs(fill = "Type")
  
  
  )

```




## **Countries** 

Showing the trend of the cases based on the dates chosen.
```{r echo=FALSE, eval=T}
inputPanel(
selectInput(inputId = "Ctr_", 
                        label = "Country of interest",
                        choices = countries_list, selected = "Germany", multiple = T   ),



 # checkboxGroupInput("month_sel", "Month",
 #                    choiceNames=Months, 
 #                    choiceValues = Months)
 
 
  checkboxGroupInput("type_dat_", "Type",
                    choiceNames=c("Confirmed", "Death", "Recovered"), 
                    choiceValues = c("confirmed", "death", "recovered"), 
                    selected =  c("confirmed", "death", "recovered")),
  

# selectInput(inputId = "years", 
#                         label = "Year",
#                         choices = years, selected = "2020"   ),

  # sliderInput("obs", "Months:",
  #   min = 1, max = 12, value = c(1,12)
  # )
#numericInput("obss", "Month", 5, min = 1, max = 12),

dateRangeInput('dateRange',
      label = 'Date range:',
      start = max(coronavirus$date- 10, na.rm = T), end = max(coronavirus$date, na.rm = T)
    )

 # sliderInput("slider2", label = "Cases:", min = 0, 
 #        max = max(coronavirus$cases, na.rm = T), 
 #        value = c(min(coronavirus$cases, na.rm = T),       max(coronavirus$cases, na.rm = T)))

#renderPrint(input$obs)
 #renderPrint(input$obss)
)
dat_Month <- reactive(
  
 coronavirus %>%   filter(   (country %in% c(input$Ctr_)) & (date>=input$dateRange[1] & date<=input$dateRange[2]) & (type %in% input$type_dat_) )%>% group_by(date, type, country) %>% summarise(cases=sum(cases),  #month=unique(month), 
                                                                                                 type=unique(type), country=unique(country)) 
   
  
)
#str(coronavirus$date)



#renderPrint(dat_Month())
 renderPlotly({
   # validate(
   #      need(input$obss, "")
   #    )
   validate(
         need(input$type_dat_, "")
       )
     
dat_Month() %>%  ggplot(aes(date, cases, color=type, shape=country))+geom_point()+ geom_line()+
  theme_bw()+
  facet_wrap(~type, scales = "free", nrow = 2, labeller = labeller(
        type = c("confirmed" = "Confirmed", "death"="Death", "recovered"="Recovered")) )+
  #theme(legend.position = "none")+
     # theme(axis.text.x = element_text(size = 12, face="bold"), 
     #                            axis.text.y = element_text(size = 12, face="bold"))+
     xlab("Month")+ ylab("Cases")+guides(color=FALSE)
   
   })



```



##

# **Most recent data**{.tabset}
## **Confirmed new cases** 


```{r echo=FALSE}

inputPanel(
selectInput(inputId = "Ctr_bar", 
                        label = "Country of interest",
                        choices = countries_list, selected = c("Germany", "England", "Austria"), multiple = T   )

)



table_inci <- reactive(
  
 coronavirus %>% filter(country %in% c(input$Ctr_bar)) %>% group_by(country) %>%  filter(date==max(date)) %>% select(country, date,type, cases) %>%  group_by(date, type, country) %>% summarise(cases=sum(cases)) %>%  mutate(date=as.character(date))
   
)


#renderPrint(table_inci())

renderPlotly({
  
table_inci() %>% filter(type %in% c("confirmed")) %>% ggplot(aes(reorder(country, cases), cases, fill=country))+
   geom_bar(stat = "identity")+#coord_flip()+
  theme(legend.position = "none")+
 geom_text(aes( label = paste(cases, date, sep=", updated on ")),  vjust = 0, hjust=0.1, size=3)+ xlab("")+facet_wrap(~type)+ coord_flip()

})

```

```{r echo=F, message=F}

new_confirmed_latest_data_world <- coronavirus  %>% group_by(country) %>%  filter(date==max(date)) %>% select(country, date,type, cases) %>%  group_by(date, type, country) %>% summarise(cases=sum(cases)) %>%  mutate(date=as.character(date)) %>% filter(type %in% c("confirmed")) %>%  filter(cases==max(cases)) 


```
### On **`r new_confirmed_latest_data_world$date`**, **`r new_confirmed_latest_data_world$country`** had the highest number of new confirmed cases of Covid-19 in the world.



## **Recovered**
```{r echo=FALSE, eval=T}

inputPanel(
selectInput(inputId = "Ctr_bar_rec", 
                        label = "Country of interest",
                        choices = countries_list, selected = c("Germany",  "Brazil","Israel"), multiple = T   )

)


table_inci_rec <- reactive(
  
 coronavirus %>% filter(country %in% c(input$Ctr_bar_rec)) %>% group_by(country) %>%  filter(date==max(date)) %>% select(country, date,type, cases) %>%  group_by(date, type, country) %>% summarise(cases=sum(cases)) %>%  mutate(date=as.character(date))
   
)


renderPlotly({
  
table_inci_rec() %>% filter(type %in% c("recovered")) %>% ggplot(aes(reorder(country, cases), cases, fill=country))+
   geom_bar(stat = "identity")+#coord_flip()+
  theme(legend.position = "none")+
 geom_text(aes( label = paste(cases, date, sep=", updated on ")),  vjust = 0, hjust=0.1, size=3)+ xlab("")+facet_wrap(~type)+ coord_flip()

})


```

```{r echo=F, message=F}

recoverd_latest_data_world <- coronavirus  %>% group_by(country) %>%  filter(date==max(date)) %>% select(country, date,type, cases) %>%  group_by(date, type, country) %>% summarise(cases=sum(cases)) %>%  mutate(date=as.character(date)) %>% filter(type %in% c("recovered")) %>%  filter(cases==max(cases)) 


```
### On **`r recoverd_latest_data_world$date`**, **`r recoverd_latest_data_world$country`** had the highest number of Covid-19 recoveries in the world.


## **Deaths**
```{r echo=FALSE, eval=T}

inputPanel(
selectInput(inputId = "Ctr_bar_death", 
                        label = "Country of interest",
                        choices = countries_list, selected = c("Germany", "France", "US"), multiple = T   )

)


table_inci_death <- reactive(
  
 coronavirus %>% filter(country %in% c(input$Ctr_bar_death)) %>% group_by(country) %>%  filter(date==max(date)) %>% select(country, date,type, cases) %>%  group_by(date, type, country) %>% summarise(cases=sum(cases)) %>%  mutate(date=as.character(date))
   
)


renderPlotly({
  
table_inci_death() %>% filter(type %in% c("death")) %>% ggplot(aes(reorder(country, cases), cases, fill=country))+
   geom_bar(stat = "identity")+#coord_flip()+
  theme(legend.position = "none")+
 geom_text(aes( label = paste(cases, date, sep=", updated on ")),  vjust = 0, hjust=0.1, size=3)+ xlab("")+facet_wrap(~type)+ coord_flip()

})


```

```{r echo=F, message=F}

death_latest_data_world <- coronavirus  %>% group_by(country) %>%  filter(date==max(date)) %>% select(country, date,type, cases) %>%  group_by(date, type, country) %>% summarise(cases=sum(cases)) %>%  mutate(date=as.character(date)) %>% filter(type %in% c("death")) %>%  filter(cases==max(cases)) 


```
### On **`r death_latest_data_world$date`**, **`r death_latest_data_world$country`** had the highest number of Covid-19 deaths in the world.

```{r setup, echo=F, message=F}
library(magrittr)
library(tidyverse)
library(plotly)
library(shiny)
library(data.table)
library(directlabels)
library(ggrepel)

library(rworldmap)

#library(tidyverse)
theme_set(theme_bw())
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

library(rgeos)

joinCountryData2Map_perso <- function (dF, joinCode = "ISO3", nameJoinColumn = "ISO3V10", 
  nameCountryColumn = "Country", suggestForFailedCodes = FALSE, 
  mapResolution = "coarse", projection = NA, verbose = FALSE) 
{
  mapWithData <- getMap(resolution = mapResolution)
  if (!is.na(projection)) 
    warning("the projection argument has been deprecated, returning Lat Lon, use spTransform from package rgdal as shown in help details or the FAQ")
  listJoinCodesNew <- c("ISO_A2", "ISO_A3", "FIPS_10_", "ADMIN", 
    "ISO_N3")
  listJoinCodesOld <- c("ISO2", "ISO3", "FIPS", "NAME", "UN")
  listJoinCodes <- c(listJoinCodesOld, listJoinCodesNew)
  if (joinCode %in% listJoinCodes == FALSE) {
    stop("your joinCode (", joinCode, ") in joinCountryData2Map() is not one of those supported. Options are :", 
      paste(listJoinCodes, ""), "\n")
    return(FALSE)
  }
  joinCodeOld <- joinCode
  if (joinCode %in% listJoinCodesOld) {
    joinCode <- listJoinCodesNew[match(joinCode, listJoinCodesOld)]
  }
  if (is.na(match(nameJoinColumn, names(dF)))) {
    stop("your chosen nameJoinColumn :'", nameJoinColumn, 
      "' seems not to exist in your data, columns = ", 
      paste(names(dF), ""))
    return(FALSE)
  }
  dF[[joinCode]] <- as.character(dF[[nameJoinColumn]])
  dF[[joinCode]] <- gsub("[[:space:]]*$", "", dF[[joinCode]])
  if (joinCode == "ADMIN") {
    dF$ISO3 <- NA
    for (i in 1:nrow(dF)) dF$ISO3[i] = rwmGetISO3(dF[[joinCode]][i])
    joinCode = "ISO3"
    nameCountryColumn = nameJoinColumn
  }
  matchPosnsInLookup <- match(as.character(dF[[joinCode]]), 
    as.character(mapWithData@data[[joinCode]]))
  failedCodes <- dF[[joinCode]][is.na(matchPosnsInLookup)]
  numFailedCodes <- length(failedCodes)
  numMatchedCountries <- nrow(dF) - numFailedCodes
  #cat(numMatchedCountries)
  failedCountries <- dF[[nameCountryColumn]][is.na(matchPosnsInLookup)]
  failedCountries <- cbind(failedCodes, failedCountries = as.character(failedCountries))
 # cat(numFailedCodes)
  if (verbose) 
    print(failedCountries)
  matchPosnsInUserData <- match(as.character(mapWithData@data[[joinCode]]), 
    as.character(dF[[joinCode]]))
  codesMissingFromUserData <- as.character(mapWithData@data[[joinCode]][is.na(matchPosnsInUserData)])
  countriesMissingFromUserData <- as.character(mapWithData@data[["NAME"]][is.na(matchPosnsInUserData)])
  numMissingCodes <- length(codesMissingFromUserData)
  #cat(numMissingCodes)
  mapWithData@data <- cbind(mapWithData@data, dF[matchPosnsInUserData, 
    ])
  invisible(mapWithData)
}

```



```{r dat, message=F, eval=TRUE, echo=F}

urlfile1="https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv"
coronavirus1 <- readr::read_csv(url(urlfile1))
countries_list <- c(levels(as.factor(coronavirus1$location)))
coronavirus_withoutworld <- coronavirus1 %>% filter(!location=="World") 
Winner_popu <- coronavirus_withoutworld %>% filter(total_vaccinations==max(total_vaccinations, na.rm = T))# & 
Winner_popu <- Winner_popu[1,1]                                   
 
Winner_Rate <- coronavirus_withoutworld %>% filter(total_vaccinations_per_hundred==max(total_vaccinations_per_hundred, na.rm = T))
Winner_Rate <- Winner_Rate[1,1]
```

##


##


# **Daily summary of Covid-19 vaccinations** {.tabset}


Up to **`r max(coronavirus1$date)`**, the country with highest population being vaccinated would be **`r Winner_popu`** while the fastest vaccination rate per hundred would be **`r Winner_Rate`**. The status is updated on a daily basis. The current time of pulling data is **`r Sys.time()`**

## **Map**

### Countries that initiated vaccination and number of shots given
```{r  echo=F, message=FALSE, error=F}


world <- ne_countries(scale = "medium", returnclass = "sf")
world$location<- world$name 

Both <- world %>% dplyr::left_join(coronavirus1, by="location") %>% 
  dplyr::select(name, location, daily_vaccinations, geometry) %>% group_by(location) %>%
  dplyr::summarise(total=sum(daily_vaccinations, na.rm = T), geometry=geometry[1]) %>% filter(total >0)

  ALLE_ <- as.factor(coronavirus1$location)
   ALLE_ = ALLE_[!ALLE_ %in% c("European Union", "World")]
  
 

selectInput(inputId = "country_wanted", 
            label = "Country", 
            choices = ALLE_, 
            selected = ALLE_, multiple = T )

dat_needed_map_gg <- reactive(
  filter(Both, location %in% input$country_wanted)
  
)

renderPlot({  
  ggplot(data = dat_needed_map_gg()) +
    geom_sf(aes(fill = total)) +
    scale_fill_viridis_c(option = "plasma", trans = "sqrt")
})
 

```

## **Latest status**

**Total number of vaccination per 100 people in the total population**
```{r echo=F, fig.height=15, fig.width=8}
ylab <- c(0.01, 0.6,0.7, 0.8,0.9,1, 1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9,2, 2.4, 2.5, 5.0, 7.5, seq(10, 10000, by=2))

vaccination_countries <- levels(as.factor(coronavirus1$location))

inputPanel(
selectInput(inputId = "Ctr__vaccin_latest", 
                        label = "Country of interest",
                        choices = vaccination_countries, 
            selected = c("Israel","United Kingdom", "Germany", "France", "United Arab Emirates"), 
            multiple = T   )
)

data_latest_gg <- reactive(
  
  
  coronavirus1 %>% filter(location %in% c(input$Ctr__vaccin_latest)) %>% group_by(location)  %>%  filter(date==max(date)) %>% select(location, date,total_vaccinations, people_vaccinated_per_hundred, daily_vaccinations_per_million, total_vaccinations_per_hundred) %>% mutate(date=as.character(date))
  
)

#renderPrint(data_latest_gg())
renderPlot({
 data_latest_gg()  %>% ggplot(aes(reorder(location, total_vaccinations), total_vaccinations, fill=location))+
   geom_bar(stat = "identity")+theme(legend.position = "none")+
 geom_text(aes( label = paste(total_vaccinations, date, sep=", updated on ")), 
          angle=45, vjust = 0, hjust=0, size=4)+  
    ylab("Total shots given")+ xlab("")+
    theme(axis.text.x = element_text(size=15, angle = 90, face = "bold"))+  scale_y_continuous(labels = paste0(ylab, "M"), 
                                                                                               breaks = 10^6 * ylab)

})



renderPlot({
 data_latest_gg()  %>% ggplot(aes(reorder(location, total_vaccinations_per_hundred), total_vaccinations_per_hundred, fill=location))+
   geom_bar(stat = "identity")+theme(legend.position = "none")+
 geom_text(aes( label = paste(total_vaccinations_per_hundred, date, sep=", updated on ")), 
          angle=45, vjust = 0, hjust=0, size=4)+  
    ylab("Total vaccination per 100 people in the total population")+ xlab("")+
    theme(axis.text.x = element_text(size=15, angle = 90, face = "bold"))

})
# table %>% filter(total_vaccinations_per_hundred>0.000000001) %>% mutate(loc_date= paste(location, date, sep=" ")) %>%  ggplot(aes(reorder(loc_date, total_vaccinations_per_hundred), total_vaccinations_per_hundred, fill=location))+
#   geom_bar(stat = "identity")+coord_flip()+theme(legend.position = "none")+
# geom_text(aes( label = paste(total_vaccinations_per_hundred, date, sep=", updated on ")),  vjust = 0, hjust=0, size=3)+  ylab("Total vaccination 100 people in the total population")+ xlab("")
# 

```

## **Overall status since vaccination start**
```{r, fig.width=40, echo=FALSE, fig.height=90, out.width="100%", out.height="100%", out.extra="100%"}
# mutate(Breaks=ifelse(total_vaccinations_per_hundred>15, "S1", ifelse(total_vaccinations_per_hundred<15 & total_vaccinations_per_hundred>10, "S2", ifelse(total_vaccinations_per_hundred<=10 &total_vaccinations_per_hundred>5, "S3", ifelse(total_vaccinations_per_hundred <=5 & total_vaccinations_per_hundred>3, "S4", ifelse(total_vaccinations_per_hundred <=3 & total_vaccinations_per_hundred>1, "S5", ifelse(total_vaccinations_per_hundred <=1, "S6", "S7"))))))) %>% filter(!is.na(Breaks))

inputPanel( dateRangeInput('dateRange',
      label = 'Date range:',
      start = max(coronavirus1$date, na.rm = T)-10, end = max(coronavirus1$date, na.rm = T)
    ),

 sliderInput("slider2", label = "Rate range:", min = 0, 
        max = max(coronavirus1$total_vaccinations_per_hundred, na.rm = T), 
        value = c(min(coronavirus1$total_vaccinations_per_hundred, na.rm = T),       max(coronavirus1$total_vaccinations_per_hundred, na.rm = T)))

)



 dat_date_range <- reactive({ filter(coronavirus1, date>=input$dateRange[1] & date<=input$dateRange[2]) %>% 
                              
                            filter(total_vaccinations_per_hundred>=input$slider2[1] & total_vaccinations_per_hundred <= input$slider2[2])
                           } )

  renderPlot(   {
    dat_date_range() %>%  
    
ggplot(aes(date, total_vaccinations_per_hundred, color=location, label=location))+geom_point()+ geom_line()+
   geom_dl(aes(label = location, size=0.5), method = list(dl.trans(x = x - 2.73, y=y+0.3), "last.points")) + theme_bw()+
  # geom_dl(aes(label = location), method = list(dl.trans(x = x - .1), "first.points"))
     theme(legend.position = "none")+ ylab("Total vaccination per hundred")+theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

})


```

## **Total Shots Given**

Total of vaccination doses administered. This is counted as a single dose, and may not equal the total number of people vaccinated, depending on the specific dose regime (e.g. people receive multiple doses). If a person receives one dose of the vaccine, this metric goes up by 1. If they receive a second dose, it goes up by 1 again.

```{r  fig.width=40, echo=FALSE, fig.height=90, out.width="100%", out.height="100%", out.extra="100%", echo=F}

ylab <- c(0.01, 0.6,0.7, 0.8,0.9,1, 1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9,2, 2.4, 2.5, 5.0, 7.5, seq(10, 10000, by=2))


selectInput(inputId = "Ctr", 
                        label = "Country of interest",
                        choices = countries_list, selected = "Germany")


 dat_Ctr <- reactive(
   coronavirus1 %>%   filter(   (location %in% input$Ctr)  )
 
)


renderPlotly({
dat_Ctr() %>% ggplot(aes(as.character(date), total_vaccinations, fill=location, group = 1))+
  geom_point()+geom_line() + facet_wrap(~location, scales = "free")+ ylab("")+ ggtitle("Total population vaccinated")+
    xlab("Date")+theme_bw() + theme(axis.text.x = element_text(angle = 90))+  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab)


})


```


## **Population Fully Vaccinated**

Data regarding people fully vaccinated is available for some countries only. 
Total number of people receiving the shots needed for the vaccine to be effective is shown. Some vaccines require 1 shot while other vaccines require 2 shots. 
```{r  fig.width=40, echo=FALSE, fig.height=90, out.width="100%", out.height="100%", out.extra="100%", echo=F, warning=FALSE, message=FALSE}



Both2 <- world %>% dplyr::left_join(coronavirus1, by="location") %>% 
  dplyr::select(name, location, people_fully_vaccinated, geometry) %>% group_by(location) %>%
  dplyr::summarise("Population Fully Vaccincated"=max(people_fully_vaccinated, na.rm = T), geometry=geometry[1]) %>% filter(`Population Fully Vaccincated` >0)





  Both2_ALLE <- as.factor(Both2$location)
   Both2_ALLE = Both2_ALLE[!Both2_ALLE %in% c("European Union", "World")]
  


selectInput(inputId = "country_wanted", 
            label = "Country", 
            choices = Both2_ALLE, 
            selected = Both2_ALLE, multiple = T )


renderPlot({  
  ggplot(data = Both2) +
    geom_sf(aes(fill = `Population Fully Vaccincated`)) +
    scale_fill_viridis_c(option = "plasma")
})


ylab <- c(0.01,0.02,0.03, 0.04,0.05, 0.1,0.2, 0.3, 0.5,0.4,0.5, 0.6,0.7, 0.8,0.9,1, 1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9,2, 2.4, 2.5, 5.0, 7.5, seq(10, 10000, by=2))


selectInput(inputId = "Ctr_fully", 
                        label = "Country of interest",
                        choices = Both2_ALLE, selected = "Germany", multiple = T)


 dat_Ctr_full <- reactive(
   coronavirus1 %>%   filter(   (location %in% input$Ctr_fully)  )
 
)


renderPlotly({
dat_Ctr_full() %>% ggplot(aes(as.character(date), people_fully_vaccinated, fill=location, group = 1, shape=location))+
  geom_point()+geom_line() + 
   # facet_wrap(~location, scales = "free")+ 
    ylab("")+ ggtitle("Total Population Fully Vaccinated")+
    xlab("Date")+theme_bw() + theme(axis.text.x = element_text(angle = 90))+  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab)


})





```

## **Per Hundred People**
Total vaccinations per 100 people in the total population of the country
```{r echo=F}


selectInput(inputId = "Ctrr", 
                        label = "Country of interest",
                        choices = countries_list, selected = "Germany")

 dat_Ctrr <- reactive(
   coronavirus1 %>%   filter(   (location %in% input$Ctrr)  )
 
)

renderPlotly({
dat_Ctrr() %>% ggplot(aes(as.character(date), total_vaccinations_per_hundred, fill=location, group = 1))+
  geom_point()+geom_line() +  ylab("")+ 
    xlab("Date") +  theme_bw()+theme(axis.text.x = element_text(angle = 90))#+  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab)


})

```



## **Per Million People**
Daily vaccinations per 1,000,000 people in the total population of the country.
```{r echo=F}


selectInput(inputId = "Ctrrr", 
                        label = "Country of interest",
                        choices = countries_list, selected = "Germany")

 dat_Ctrrr <- reactive(
   coronavirus1 %>%   filter(   (location %in% input$Ctrrr)  )
 
)

renderPlotly({
dat_Ctrrr() %>% ggplot(aes(as.character(date), daily_vaccinations_per_million, fill=location, group = 1))+
  geom_point()+geom_line() +  ylab("")+ 
    xlab("Date") +theme_bw()+ theme(axis.text.x = element_text(angle = 90)) #+  scale_y_continuous(labels = paste0(ylab, "M"), breaks = 10^6 * ylab)


})

```




## **Latest Summary data**
```{r echo=F}

table_lat <- coronavirus1 %>% group_by(location) %>%  filter(date==max(date)) %>% select(location, date,total_vaccinations, people_vaccinated_per_hundred, daily_vaccinations_per_million) %>% arrange(desc(date))%>% mutate(date=as.character(date))

renderTable(table_lat)

```





